Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-04-08 WSSSPE4_report/WSSSPE4_report.tex
author changes

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Alice~Allen$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nunez-Corrales$^{(9)}$
Anshu~Dubey$^{(10)}$,
R.~Stuart~Geiger$^{(11)}$,
Jonah~Miller$^{(12)}$,
Emily~Chen$^{(13)}$,
Wolfgang~Bangerth$^{(14)}$%,
%\\Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: 0000-0002-1021-3101}
%
\thanks{{}$^{(5)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(6)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(7)}$ University of Virginia, Charlottesville, VA, USA; jeansalac@virginia.edu; ORCID: 0000-0001-5971-9333}
%
\thanks{{}$^{(8)}$ University of Edinburgh, UK; N.ChueHong@epcc.ed.ac.uk;
ORCID: 0000-0002-8876-7606}
%
\thanks{{}$^{(9)}$ Illinois Informatics Institute (I3) and National Center for Supercomputing Applications (NCSA), University of Illinois at Urbana-Champaign, IL, USA;
nunezco2@illinois.edu;
ORCID: 0000-0003-4342-6223}
%
\thanks{{}$^{(10)}$ Mathematics and Computer Science Division,
Argonne National Laboratory,
Lemont, IL, USA \& 
University of Chicago, 
Chicago, IL, USA;
Adubey@anl.gov;
ORCID: 0000-0003-3299-7426}
%
\thanks{{}$^{(11)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(12)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph, 
Guelph, ON, Canada; 
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(13)}$ University of Illinois at Urbana-Champaign, USA; echen35@illinois.edu; ORCID: 0000-0003-2578-0296}
%
\thanks{{}$^{(14)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Ray Idaszak$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nunez-Corrales$^{(9)}$,
Alice~Allen$^{(10)}$,
R.~Stuart~Geiger$^{(11)}$,
Jonah~Miller$^{(12)}$,
Emily~Chen$^{(13)}$,
Anshu~Dubey$^{(14)}$,
Wolfgang~Bangerth$^{(15)}$%,
%\\Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: 0000-0002-1021-3101}
%
\thanks{{}$^{(5)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(6)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org; ORCID: \todo{}}
%
\thanks{{}$^{(7)}$ University of Virginia, Charlottesville, VA, USA; jeansalac@virginia.edu; ORCID: 0000-0001-5971-9333}
%
\thanks{{}$^{(8)}$ University of Edinburgh, UK; N.ChueHong@epcc.ed.ac.uk;
ORCID: 0000-0002-8876-7606}
%
\thanks{{}$^{(9)}$ Illinois Informatics Institute (I3) and National Center for Supercomputing Applications (NCSA), University of Illinois at Urbana-Champaign, IL, USA;
nunezco2@illinois.edu;
ORCID: 0000-0003-4342-6223}
%
\thanks{{}$^{(10)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(11)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(12)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph, 
Guelph, ON, Canada; 
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(13)}$ University of Illinois at Urbana-Champaign, USA; echen35@illinois.edu; ORCID: 0000-0003-2578-0296}
%
\thanks{{}$^{(14)}$ Mathematics and Computer Science Division,
Argonne National Laboratory,
Lemont, IL, USA \& 
University of Chicago, 
Chicago, IL, USA;
Adubey@anl.gov;
ORCID: 0000-0003-3299-7426}
%
\thanks{{}$^{(15)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}
